---
title: "Final_Project _Draft"
author: "Ying Sun"
date: "5/3/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# New Line
```
# Intro

## What
This project is about US winter Olympic Gold medalists for the past 20 years.
## Why
The reason I chose this topic is because winter Olympic just finished this year in Beijing, China. I did see some improvements of Chinese athletes this year, it seems that they won some gold medals that were big challenges for them in the past. I am curious to know how has Team US been doing, for example, some of the winter games Team US have been quite good at 10 years ago, are they still leaders?
## How
I  created an excel file which contains data of US Winter Olympics Gold Medalists from year 2002 to year 2022.I found these data from Wikipedia.
# Body


My excel file has the following columns:
```{r}
library(readxl)
winter_olympics <- read_excel("C:/Users/vicky/Downloads/Ying-s-631-final-p/winter olympics.xlsx")
```

```{r}
names(winter_olympics)
```
1. I would like to see how many gold medals did Team US won for the past 20 years?
```{r}
table(winter_olympics$`Gold Medal`)
```
There are total of 54 gold medals Team Us won in the past 20 years.

2.  I would like to compare women vs. men who won more medals overall and compare the ratios.
```{r}
table(winter_olympics$WOMEN)
```
```{r}
table(winter_olympics$MEN)
```
```{r}
table(winter_olympics$WOMEN)/table(winter_olympics$`Gold Medal`)
```

```{r}
table(winter_olympics$MEN)/table(winter_olympics$`Gold Medal`)
```
As we can see the above calculations, overall, men won more gold medals than women for the past 20 years in winter Olympics.

3. I want to find out which year did TEAM US won the most Gold Medals in Winter Olympics?
```{r}
aggregate(`Gold Medal` ~ YEAR, data=winter_olympics, FUN=sum)
```
As we can tell that Team US won the most gold medals in year 2002 winter olympics with a total of 10. 
Year 2022 Team US won least gold medals, with a total of 8. 

4. below are some bar plots I use to further represent the portion of women vs. men in winter olympics.
```{r}
barplot(table(winter_olympics$MEN))
```
```{r}
barplot(table(winter_olympics$WOMEN))
```
```{r}
gender_sport <- table(winter_olympics$GENDER, winter_olympics$YEAR)
mosaicplot(gender_sport)
```
5. below are the box plots of showing gender portion of different Olympic games
```{r}
boxplot(winter_olympics$YEAR ~ winter_olympics$GENDER)
```
```{r}
boxplot(winter_olympics$`Gold Medal` ~ winter_olympics$GENDER)
```
```{r}
hist(winter_olympics$`Gold Medal`)
```


6.  I would like to see which sports Team US won the most medals,I will use tidyverse to demonstrate this.

```{r}
library(tidyverse)
winter_olympics%>% group_by(SPORT)%>% summarise(n=n())
```
As we can see from the above, Team US won the most gold medals in Snowboarding with 18 gold medals in total.

```



# Topics From Class

## Topic 1:
R Markdown-I really like how many functions R Markdown has offered. We can easily convert the files to word, pdf and html by using Knit. We can also insert R commands in between our texts and run it by single sentence or run the whole commands.

## Topic 2:
Github-we can push R Markdown files on Github, share a link, and others can read our files. 

## Topic 3:
Probability-I used probability calculation for my project to show women and men's ratio in winter olympic games.  

## Topic 4:
Tidyservice-I used tidyservice to show which sport Team USA won the most gold medals in winter olympics, because the column sport are not numbers, they are strings, I couldn't get it to work in the basic R, tidyservice has the functions to group strings. 

## Topic 5:
table command-I used this command to show a summary of how many men or women won the onlympic gold medals. 

# Conclusion
This final project helps me review some of the knowleges or commands we learned in class and assignments, such as R markdown, Tidyservice, probability, barplots, mosiacplot, etc.  I think this is a good way to put what we learned into practices.