---
title: "Final_Project _Draft"
author: "Ying Sun"
date: "5/3/2022"
output: pdf_document
---


# Intro
The Winter Olympic Game is a major international multi-sport event held once every four years for soprts practiced on snow and ice.

## What
This is just simple project about US winter Olympic Gold medalists for the past 20 years.

## Why
The reason I chose this topic is because winter Olympic just finished this year in Beijing, China. I did see some improvements of Chinese athletes this year, it seems that they won some gold medals that were big challenges for them in the past. I am curious to know how has Team US been doing.

## How
I  created an excel file which contains data of US Winter Olympics Gold Medalists from year 2002 to year 2022.I found these data from Wikipedia.I will use R commands to show some statistics and graphs.

# Body

**I first imported my excel data by using the read_excel, and My excel file has the following columns:**

```{r}
library(readxl)
winter_olympics <- read_excel("winter olympics.xlsx")
```

```{r}
names(winter_olympics)
```

**1. I would like to see how many gold medals did Team US won for the past 20 years?**
```{r}
table(winter_olympics$`Gold Medal`)
```
**There are total of 54 gold medals Team Us won in the past 20 years.**


**2.  I would like to compare women vs. men who won more medals overall and compare the ratios.**
```{r}
table(winter_olympics$WOMEN)
```
```{r}
table(winter_olympics$MEN)
```
**Based on the summaries, men and women each have 59 athletes, there were 22 women won the gold medals and 28 men won, the ratio calculations are as following:**

```{r}
table(winter_olympics$WOMEN)/table(winter_olympics$`Gold Medal`)
```

```{r}
table(winter_olympics$MEN)/table(winter_olympics$`Gold Medal`)
```
**As we can see the above calculations, overall, men have higher ratio of winning gold medals than women for the past 20 years in winter Olympics.**

**3. I want to find out which year did TEAM US won the most Gold Medals in Winter Olympics?**

```{r}
aggregate(`Gold Medal` ~ YEAR, data=winter_olympics, FUN=sum)
```

**As we can tell that Team US won the most gold medals in year 2002 winter Olympic with a total of 10 gold medals. Year 2022 Team US won least gold medals, with a total of 8. But overall, Team US did not have a big difference in terms of winning the number of gold medals at each Olympic game.**

**4. below is the mosaicplot I use to further represent the portion of gender winning gold medals in winter olympics in different year.**

```{r}
gender_sport <- table(winter_olympics$GENDER, winter_olympics$YEAR)
mosaicplot(gender_sport, border ="brown", col="#69b3a2")
```

**As the mosaicplot shows women won more gold medals in year 2002,2014, 2018 and 2022.** 


**5. below are the box plots of showing gender portion of different Olympic games**

```{r}
boxplot(winter_olympics$YEAR ~ winter_olympics$GENDER, border= "purple", col="pink")
```
```{r}
boxplot(winter_olympics$`Gold Medal` ~ winter_olympics$GENDER, border="purple", col="pink")
```

6. Below is the the histogram showing the Frequency of each year of Olympic games.

```{r}
hist(winter_olympics$YEAR, density=c(5,10,20,30,7) , angle=c(0,45,90,11,36) , col="brown")
```
```{r}
table(winter_olympics$YEAR)
```


**6.I would like to see which sports Team US won the most medals,I will use tidyverse to demonstrate this.**

```{r}
library(tidyverse)
winter_olympics%>% group_by(SPORT)%>% summarise(n=n())
```


**As we can see from the above, Team US won the most gold medals in Snowboarding with 18 gold medals in total.**



# Topics From Class

## Topic 1:
R Markdown-I really like how many functions R Markdown has offered. We can easily convert the files to word, pdf and html by using Knit. We can also insert R commands in between our texts and run it by single sentence or run the whole commands.

## Topic 2:
Github-I am still a beginner for Github, I learned how to push R markdown files to Github to share with others.I am sure there are ohter cool functions in Github, I just need to explore more.

## Topic 3:
Probability-I used probability calculation for my project to show women and men's ratio in winter olympic games.  

## Topic 4:
Tidyservice-I used tidyservice to show which sport Team USA won the most gold medals in winter olympics, because the column sport are not numbers, they are strings, I couldn't get it to work in the basic R, tidyservice has the functions to group strings. 

## Topic 5:
table, histogram, barplots-I used table command to show a summary of how many men or women in total won the Olympic gold medals. Histogram and barplots help show the different graphs we can use in R studio.

# Conclusion
This final project really helps me review some of the knowledge and skills  we covered in class, such as R markdown, Tidy service, probability calculations, barplots, etc.  I think this is a good way to put what we learned into practices.I also learned how to add colors to my graphs by reviewing other peers' projects. I learned a lot from the  final project feedback section as well, everyone's project is unique and covered different aspects of what we learned during this semester. I do face some challenges, for example, I haven't figured out how to add colors to my barplot graphs, but overall, this is a great learning experience for me. 