---
title: "Final_Project _Draft"
author: "Ying Sun"
date: "5/3/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# New Line
```
# Intro

## What
This project is about US winter Olympic Gold medalists for the past 20 years.
## Why
The reason I chose this topic is because winter Olympic just finished this year in Beijing, China. I did see some improvements of Chinese athletes this year, it seems that they won some gold medals that were big challenges for them in the past. I am curious to know how has Team US been doing, for example, some of the winter games Team US have been quite good at 10 years ago, are they still leaders?
## How
I  created an excel file which contains data of US Winter Olympics Gold Medalists from year 2002 to year 2022.I found these data from Wikipedia.
# Body


My excel file has the following columns:
```{r}
names(winter_olympics)
```
First, I would like to see how many gold medals did Team US won for the past 20 years?
```{r}
table(winter_olympics$`Gold Medal`)
```
Second, I would like to compare women vs. men who won more medals overall and compare the ratios.
```{r}
table(winter_olympics$WOMEN)
```
```{r}
table(winter_olympics$MEN)
```
```{r}
table(winter_olympics$WOMEN)/table(winter_olympics$`Gold Medal`)
```

```{r}
table(winter_olympics$MEN)/table(winter_olympics$`Gold Medal`)
```


Challenges: 1). I would like to see which sports Team US won the most medals, but I don't know how to show this. 2). I also want to show which year US won the most/least medals, I tried the command below, but it only showed integer(0):
```{r}
 X <- (winter_olympics$WOMEN+winter_olympics$MEN)
which.max(X)
```

# Topics From Class

## Topic 1:
R Markdown-I really like how many functions R Markdown has offered. We can easily convert the files to word, pdf and html by using Knit. We can also insert R commands in between our texts and run it by single sentence or run the whole commands.  
## Topic 2:
Github-we can push R Markdown files on Github, share a link, and others can read our files. 
## Topic 3:
Probability-I will use probability calculations several times for my project, we have used these calculations for our chapter 3 homework.
## Topic 4:
Barplots-a common way to display a single categorical variable, this will be a good visualization for my project.
## Topic 5:
Histograms-convenient for describing the shape of the data distribution.
# Conclusion
The data proves my initial hypothesis: 1).Men won more gold medals in winter Olympic than women.
by doing this project, I have used some of the knowledge we discussed during class: probability calculation, publish R markdown in Github, there are still some parts of this project I need to figure out why the commands didn't work. I talked in the challenge section. Hopefully I can figure them out in the end.